### 2024-07-11 cognitive-bias.qmd
29249710 - figure labels
20240711 - conclusion

Three important heuristics used in judgment and prediction in the face of uncertainty include [@Tversky1974]:

@@

Examples of cognitive biases that result from one or more of these heuristics include:

@@

Players' performance in fantasy football, and human behavior more generally, is complex and multiply determined.
No one can predict accurately how all players will perform.
Remain humble in your predictions; do not be more confident than you should be.

@@

Dunning–Krueger Effect. Adapted from <https://commons.wikimedia.org/wiki/File:Effet_Dunning-Kruger.svg>.
:::

@@

Dunning–Krueger Effect. Adapted from <https://commons.wikimedia.org/wiki/File:Dunning-kruger_effect_-_percentile.svg>.
:::

@@

Fallacies are mistaken beliefs that are often due to heuristics and cognitive biases.
Examples of fallacies include:

@@

@@

@@

>>>>

As described [above](#sec-cognitiveBiasOverview), heuristics are mental shortcuts that people use to handle the overwhelming amount of information to process.
Three important heuristics used in judgment and prediction in the face of uncertainty include [@Tversky1974]:

@@

As described [above](#sec-cognitiveBiasOverview), cognitive biases are systematic errors in thinking.
Cognitive biases are often due to the use of [heuristics](#sec-heuristics).
Examples of cognitive biases that result from one or more of these heuristics include:

@@

Players' performance in fantasy football, and human behavior more generally, is complex and multiply determined.
No one can predict accurately how all players will perform.
Remain humble in your predictions; do not be more confident than is warranted.
If you approach the task of prediction with humility, you may be more able to be flexible and more willing to consider other players who you can draft for good value.

@@

Dunning–Krueger Effect: Confidence as a Function of Competence. Adapted from <https://commons.wikimedia.org/wiki/File:Effet_Dunning-Kruger.svg>.
:::

@@

Dunning–Krueger Effect: Perceived Performance as a Function of Actual Performance. Adapted from <https://commons.wikimedia.org/wiki/File:Dunning-kruger_effect_-_percentile.svg>.
:::

@@

As described [above](#sec-cognitiveBiasOverview), fallacies are mistaken beliefs and flawed reasoning.
Fallacies are often due to the use of [heuristics](#sec-heuristics) and to [cognitive biases](#sec-cognitiveBiases).
Examples of fallacies include:

@@

We discuss ways to counteract the base rate fallacy in @sec-baseRates.

@@

It is important consider whether such a string of strong performances are outliers and if the player may, in future games, [regress to the mean](#sec-fallaciesRegression).
When considering whether strong performances are outliers and may [regress to the mean](#sec-fallaciesRegression), it is valuable to consider whether the player's health, skill, or situation has appreciably changed (compared to the player's earlier, weaker performances).
Is the player finally fully healthy?
Has the player appreciably improved in some skill that will benefit them in future games?
Has the player's long-term situation improved, such as moving up the depth chart, or receiving more carries/targets that is not tied to a specific opponent or game script?
Or, alternatively, do the improvements appear to be driven by transient, game-specific factors, such as a the health of a teammate, the opponents they played, or the game script that ensued?
If long-term outlook of the player has appreciably changed due to changes in the [fundamentals of a player's value](#sec-playerEvaluation), such as their [health](#sec-evalHealth), [skill](#sec-skill), or [situation](#sec-evalSituation), it is less likely that such performance improvements will [regress](#sec-fallaciesRegression) over the long run.

@@

In conclusion, there are many [heuristics](#sec-heuristics), [cognitive bias](#sec-cognitiveBiases), and [fallacies](#sec-fallacies) that people engage in when making judgments and predictions.
It is prudent to be aware of these common biases and to work to counteract them.
For instance, look for information that challenges or disconfirms your beliefs, and work to incorporate this information into your beliefs.
Do your best to pursue observation, data analysis, and data interpretation with an open mind.
You never know what important information you might discover if you go in with an open mind.
Pay attention to [fundamentals of a player's value](#sec-playerEvaluation), such as their [health](#sec-evalHealth), [skill](#sec-skill), or [situation](#sec-evalSituation) when considering whether a player's performance may [regress to the mean](#sec-fallaciesRegression).
If the strong performances appear to be driven by transient, game-specific factors, such as a the health of a teammate, the opponents they played, or the game script that ensued, future performances may be more likely to [regress to the mean](#sec-fallaciesRegression).
In general, people tend to be [overconfident](#sec-cognitiveBiasesOverconfidence) in their predictions.
Approach the task of prediction with humility; no one is consistently able to accurately predict how well players will perform.

### 2024-07-11 player-evaluation.qmd
20240627 - sessionInfo() for reproducibility
20240627 - sessionInfo()
20240711 - conclusion

@@

>>>>

## Skill {#sec-skill}

When scouting players, scouts consider not only the player's [athletic profile](#sec-evalAthleticProfile), but also their position-relevant skill.
For instance, how good are they are reading the defense, passing the ball, running routes, catching balls, making defenders miss tackles, taking care of the ball, consistency, etc.
Scouting and evaluating skill is a complicated endeavor, and even the professional scouts frequently make mistakes in their evaluations and predictions.
You can certainly read skill evaluations about various players; however, unlike metrics of athletic profile, we do not have direct access to the player's underlying skill.
Some may say, "You know it when you see it."
But, this is not particularly useful when trying to identify players who are undervalued or overvalued—because the skill evaluations are likely already "baked into" a player's projections.
Because we do not have direct access to a player's skill, we tend to rely on indirect metrics of their ability, such as [historical performance](#sec-evalHistoricalPerformance).

@@

::: {.content-visible when-format="html"}

## Session Info {#sec-playerEvaluationSessionInfo}

```{r}
sessionInfo()
```

:::
